---
title: "tarantino"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

The purpose of this script is to scrape Reddit and critical review sites to measure the buzz around upcoming and previous movies. It will then compile these movies into a spreadsheet and analysis will be conducted to predict how much revenue a future movie release will make on it's opening weekend.



## Initialization

Importing the necessary packages that will be used in this project.
  - rvest
      - used for web scraping
  - RedditExtratoR
      - used for scraping Reddit posts and comments

```{r init}

library("rvest")
library("RedditExtractoR")

```

```{r scraping reddit}

movieTitle <- "Bohemian Rhapsody"

redditData <- get_reddit(search_terms = movieTitle, subreddit = "movies", page_threshold = 2, sort_by = "comments")

```

```{r seperating out the posts}

totalPostsCount <- 0

for (id in redditData$id) {
  if (id == 1) {
    
    totalPostsCount = totalPostsCount + 1
  }
  
}


posts <- data.frame(
  "post" = character(totalPostsCount),
  "number_of_comments" = integer(totalPostsCount),
  "post_score" = integer(totalPostsCount),
  "average_comment_score" = integer(totalPostsCount),
  "total_comment_score" = integer(totalPostsCount),
  stringsAsFactors = FALSE
  
  #totalPostsCount
)

postsIndex <- 0
redditDataRowCounter <- 0

comment_count <- 0
commentAverage <- 0

for (id in redditData$id) {
  if (id == 1) {

    posts$post[postsIndex] <- redditData$title[redditDataRowCounter]
    posts$number_of_comments[postsIndex] <- redditData$num_comments[redditDataRowCounter]
    posts$post_score[postsIndex] <- redditData$post_score[redditDataRowCounter]
    
    postsIndex = postsIndex + 1
    comment_count <- 0
    commentAverage <- 0
  }
  
  
  
  if (id != 1) {
    
    commentAverage <- commentAverage + redditData$comment_score[redditDataRowCounter]
    posts$average_comment_score[postsIndex] <- commentAverage / comment_count
    posts$total_comment_score[postsIndex] <- commentAverage
    comment_count = comment_count + 1
    
    
  }
  
  redditDataRowCounter = redditDataRowCounter + 1
}


```

```{r}

write.csv(posts, file="test.csv")


```

